\section*{Open cover letter}
To whom it may concern
\par
For the past 20 years I’ve been genuinely interested in following IT industry trends. Currently passionate about Python for backend solutions and spatial data analysis while proficient with Flutter for frontend development. I became curious when browsing through your portfolio and checking projects involving geo-spatial data. I believe that that’s where I might be useful as a new programmer in the Computas company. From Knut Hjelmseth I have heard that your company is always in need of capable developers so I’d like to put my name in the hat.
  \par
  For the past 2 years I have been working as an executive officer at the Natural History Museum under the University of Oslo developing a new citizen science project \textit{Natur i Endring}. My job was to develop full-stack solution for geospatial data gathering through both Android and iOS smart phones. Even though being the only developer on the project, I was closely collaborating with a small team of dedicated designers, scientists and project coordinators. The project was successfully launched in 2018 and gained more than 3000 users within the first year, together with a multitude of mentions in various newspapers and TV networks \cite{newspaper1,newspaper2,newspaper3,newspaper4,newspaper5,tv1,tv2}. 
  \par
  During my career I always tried to apply IT solutions to environmental issues. An example is my bachelor’s thesis \cite{Torma_Solár_2015}, where I extracted geospatial data about different cadastres and used principal component analysis to identify trends in the region. Also, during my master thesis \cite{msc} I have done statistical analysis of data obtained through Natur i Endring project to identify viability of this kind of data collection. Many of my personal projects concern geographical analysis of publicly available data. 
\par
I’m used to having scientific or technical talks for different types of audience. I consider myself to be swiftly adapting to new workflows and easy to work with. I like new challenges and am focused on finding the best solutions. I would very much like to use my dedication, my knowledge and my experience to solve the tasks required in Computas. I will gladly provide any additional information about myself and my work on a potential interview.