\cvsection{Experience}

\begin{cventries}
  \cventry
    {Head engineer} % Job title
    {University of Oslo} % Organization
    {Oslo, Norway} % Location
    {April. 2018 - PRESENT} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Development of \textit{\underline{\href{https://l.ead.me/batwGC}{Natur i Norge Guide}}} in collaboration with \underline{\href{https://www.nhm.uio.no/om/organisasjon/forskning-samlinger/personer/runeho/}{Rune Harvorsen}} and \underline{\href{https://www.artsdatabanken.no/}{Artsdatabanken}}. The app is a concise synthesis of \textit{Natur i Norge} textbooks presented in an interactive manner. It's main objective is to help professional mappers identify which nature type they encounter while mapping in the field. The app is written in Flutter and available on the \underline{\href{https://natur-i-norge.no/}{web}}, \underline{\href{https://play.google.com/store/apps/details?id=no.naturinorge.naturinorge_guide}{Android}} and \underline{\href{https://apps.apple.com/us/app/natur-i-norge-guide/id1495898327}{iOS}}}
      \end{cvitems}
    }
  \cventry
    {Executive Officer} % Job title
    {University of Oslo} % Organization
    {Oslo, Norway} % Location
    {Jan. 2018 - PRESENT} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Development and maintenance of a citizen science project called \textit{\underline{\href{https://naturiendring.no}{Natur i Endring}}} (made in collaboration with \underline{\href{https://www.dnt.no/}{DNT}}, \underline{\href{https://www.nhm.uio.no/}{NHM}} and \underline{\href{https://www.norskfjellsenter.no/}{Norsk Fjellsenter}} and financed by \underline{\href{https://www.sparebankstiftelsen.no/no}{Sparebankstiftelsen}}). The project consists of a mobile app for \underline{\href{https://play.google.com/store/apps/details?id=no.naturiendring.naturiendring}{Android}} and \underline{\href{https://itunes.apple.com/us/app/natur-i-endring/id1382400241?mt=8&uo=4}{iOS}} (written in Flutter). Alongside the frontend apps, I created and now maintain kubernetes cluster (running on Google Kubernetes Engine) with Django backend and PostGis database to handle the data collection and automated data analysis. This project has been awarded \textit{\underline{\href{https://www.forskerforbundet.no/om-oss/hjernekraftprisen/vinnere/2019-vinnerbidragene/}{Forskerforbundets Hjernekraft prisen}}} by the The Norwegian Association of Researchers}
      \end{cvitems}
    }



  \cventry
    {Linux administration lecturer} % Job title
    {Hewlett-Packard} % Organization
    {Prague, Czech Republic} % Location
    {Jul. 2009 - Aug. 2010} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Lecturing one week long courses of linux administration for an enterprise's IT staff. Lectures were designed as a interactive way of learning starting with basic commands and system overview, and ending with kernel compilation}
      \end{cvitems}
    }

    \cventry
    {Web developer} % Job title
    {Self-employed} % Organization
    {Martin, Slovakia} % Location
    {Jan. 2008 - Apr. 2019} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Developed multitude of webpages based on WordPress framework for small local businesses. Here are some examples.}
        \subitem {\underline{\href{https://sjoormen.no/}{sjoormen.no}} - Webpage for promotion of Garvikstrondi camping (Seljord, Norway)}
        \subitem {\underline{\href{http://classervice.sk/en/}{classervice.sk}} - Webpage for local taxi service (Martin, Slovakia)}
      \end{cvitems}
    }

  \cventry
    {IT technician} % Job title
    {Apple retailer} % Organization
    {Martin, Slovakia} % Location
    {Apr. 2007 - Aug. 2008} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Worked as an IT technician for small Apple retailer.}
      \end{cvitems}
    }


\end{cventries}
